Hopkins M & SD

### 2024-04-02 reconstruct_effect_sizes/hopkins_es.Rmd
add other stuff

```{r}
library(tidyverse)
library(here)
```
Key effect is that explantion level predicts rating (this is in an lm, but we're doing it outside for SMD here)

@@

```{r}
dat <- read_csv(here("hopkins_raw.csv")) |>  # this has 147 unique IDs so seems likely to be the mturk sample post attention check?
  select(ID, rating, condition) |> 
  group_by(ID, condition) |> 
  summarize(rating=mean(rating)) |> 
  group_by(condition) |> 
  summarize(m=mean(rating), s=sd(rating))

>>>>

```{r}
library(tidyverse)
library(here)
```
Key effect is that explanation level predicts rating (this is in an lm, but we're doing it outside for SMD here)

@@

```{r}
dat <- read_csv(here("reconstruct_effect_sizes/hopkins_raw.csv")) |>  # this has 147 unique IDs so seems likely to be the mturk sample post attention check?
  select(ID, rating, condition) |> 
  group_by(ID, condition) |> 
  summarize(rating=mean(rating)) |> 
  group_by(condition) |> 
  summarize(m=mean(rating), s=sd(rating))

### 2024-04-02 reconstruct_effect_sizes/schechtman_es.Rmd
add other stuff

thing1 <- readMat(here("DataTest1.mat"))

@@

thing2 <- readMat(here("DataTest2.mat"))

@@

thing3 <- readMat(here("DataTest1_cases 4 13 18 omitted.mat")) # has 1-22

@@

# figure out rescue
full_data <- read_csv(here("subject_data_final_full_processed.csv"))

>>>>

thing1 <- readMat(here("reconstruct_effect_sizes/DataTest1.mat"))

@@

thing2 <- readMat(here("reconstruct_effect_sizes/DataTest2.mat"))

@@

thing3 <- readMat(here("reconstruct_effect_sizes/DataTest1_cases 4 13 18 omitted.mat")) # has 1-22

@@

# figure out rescue
full_data <- read_csv(here("reconstruct_effect_sizes/subject_data_final_full_processed.csv"))
